Hydrodynamics and rheology of weakly adhesive vesicle doublets

### 2019-02-03 vesicle_code/docs/adhesion/adhesion.tex
added the multiple body simulation

We further characterize the dynamics by examining the vorticity and
total force on the vesicles.

@@

>>>>

We further characterize the rotating dynamics of a doublet by examining
the vorticity and total force on the vesicles.  In Figure~\ref{}

\begin{figure}[htp]
  \includegraphics[height = 0.26\textwidth,trim={6cm 1cm 5cm
  0cm},clip]{figs/extensionalVorticity01.png}
  \includegraphics[height = 0.26\textwidth,trim={6cm 1cm 5cm
  0cm},clip]{figs/extensionalVorticity02.png}
  \includegraphics[height = 0.26\textwidth,trim={6cm 1cm 5cm
  0cm},clip]{figs/extensionalVorticity03.png}
  \includegraphics[height = 0.26\textwidth,trim={6cm 1cm 5cm
  0cm},clip]{figs/extensionalVorticity04.png}
  \includegraphics[height = 0.26\textwidth,trim={5cm 1cm 2cm
  0cm},clip]{figs/extensionalVorticity05.png} \\
  \includegraphics[height = 0.26\textwidth,trim={6cm 1cm 5cm
  0cm},clip]{figs/extensionalVorticity06.png}
  \includegraphics[height = 0.26\textwidth,trim={6cm 1cm 5cm
  0cm},clip]{figs/extensionalVorticity07.png}
  \includegraphics[height = 0.26\textwidth,trim={6cm 1cm 5cm
  0cm},clip]{figs/extensionalVorticity08.png}
  \includegraphics[height = 0.26\textwidth,trim={6cm 1cm 5cm
  0cm},clip]{figs/extensionalVorticity09.png}
  \includegraphics[height = 0.26\textwidth,trim={5cm 1cm 2cm
  0cm},clip]{figs/extensionalVorticity10.png}
  \caption{\label{fig:extensionalVorticity} The vorticity and total
  force of two vesicles in a doublet.  The reduced area is $A = 0.7$,
  the extensional rate is $\chi = 0.7$, the adhesion length scale is
  $\delta = 0.4$, and the Hamaker constant is $H_0 = 0.7$.  When the
  doublet first starts to rotate, the net total force points in the
  direction of the diverging direction.  Next, there is a shearing
  motion between the vesicles that results in a recoil type motion near
  $t=295$.  Finally, the vorticity and the flow between the vesicles
  approaches zero and the result is a fluid trap containing the
  doublet.}
\end{figure}

@@

\begin{figure}[htp]
  \centering
  \includegraphics[width=0.24\textwidth]{figs/relaxationManyVes_Snapshot01.pdf}
  \includegraphics[width=0.24\textwidth]{figs/relaxationManyVes_Snapshot02.pdf}
  \includegraphics[width=0.24\textwidth]{figs/relaxationManyVes_Snapshot03.pdf}
  \includegraphics[width=0.24\textwidth]{figs/relaxationManyVes_Snapshot04.pdf} \\
  \includegraphics[width=0.24\textwidth]{figs/relaxationManyVes_Snapshot05.pdf}
  \includegraphics[width=0.24\textwidth]{figs/relaxationManyVes_Snapshot06.pdf}
  \includegraphics[width=0.24\textwidth]{figs/relaxationManyVes_Snapshot07.pdf}
  \includegraphics[width=0.24\textwidth]{figs/relaxationManyVes_Snapshot08.pdf}
  \caption{\label{figs:relaxationManyVes} Many vesicles suspended ...}
\end{figure}
